Summary

### 2015-10-23 inst/examples/summary.Rmd
fixed some fields

missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

>>>>

# Need to use this trick to have NAs for all data types
missing <- 100*apply(df, 2, function (x) {mean(is.na(gsub("^NA$", NA, as.character(x))))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])

theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```
